\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-21 icra-2021.tex
and we have a proof! (and a theorem that seems to work)

In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption). An observation summarized in the following Lemma, where we use norm to compare two energy coefficients vectors.

\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Given two time instants $k_1,k_2\in[t_f]$
  \begin{equation}
    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
  \end{equation}
\end{lem}
\begin{proof}
  *
\end{proof}

\subsection{Energy evolution due to computations}
\label{sec:computations-model}

@@

\begin{thm}[State output linearity]\label{thm:state-vs-energy}
  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, and assume Assumption~\ref{assm:periodic} holds. Likewise in Lemma~\ref{lem:state-vs-energy}, the model behaves ideally. 
  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$ and $\mathbf{u}_k^a$ allows to produce stage $\mathcal{M}_{k+1}$ from $\mathcal{M}_k\,\forall k\in[t_f-1]$.
\end{thm}
\begin{proof}
  *\\
\end{proof}

>>>>

%In the case of the system behaving ideally (i.e., with no uncertainty), we expect a state (energy coefficients) evolving accordingly to its output (instantaneous energy consumption). An observation summarized in the following Lemma, where we use norm to compare two energy coefficients vectors.

%\begin{lem}[State, output proportionality]\label{lem:state-vs-energy}
%  Suppose the system of Equation~(\ref{eq:state-perf}) evolves with no uncertainty ($\mathbf{w}=\mathbf{0},v=0$) and Assumption~\ref{assm:periodic} holds. Then
%  \begin{equation}
%    \|\mathbf{q}_{k_1}\|\geq\|\mathbf{q}_{k_2}\|\iff y_{k_1}\geq y_{k_2}.
%  \end{equation}
%\end{lem}
%\begin{proof}
%  Suppose $y_{k_1}\geq y_{k_2}$ is true. Given $k=k_1, k+n=k_2$, $y_{k}=\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}$. Moreover, the time evolution of the model in Equation~(\ref{eq:state-perf}) can be expressed $y_{k+n}=(\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1(n)\alpha_{k,1}+\dots+p_r(n)\alpha_{k,r}$, where $p_r(n):=\prod_{i=1}^{n/2}{r^3/\xi^3}$ depends on the order of a given coefficient and $n$. 
%  Hence, $\alpha_{k,0}+\alpha_{k,1}+\dots+\alpha_{k,r}\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})+p_1\alpha_{k,1}+\dots+p_r\alpha_{k,r}$.
%
%  The magnitudes are $\|\mathbf{q}_{k}\|=(\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2)^{1/2}$ and $\|\mathbf{q}_{k+n}\|=((\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2(n)\alpha_{k,1}^2+p_1^2(n)\beta_{k,1}^2+\dots+p_r^2(n)\alpha_{k,r}^2+p_r^2(n)\beta_{k,r}^2)^{1/2}$.
%  By still inspecting the Equation~(\ref{eq:state-perf}), the coefficient $p_r^2(n)\beta_{k,r}^2$ can be expressed as a function of coefficients $\alpha$, $p_r^2(n)\beta_{k,r}^2=$
%  
%  Hence $\alpha_{k,0}^2+\alpha_{k,1}^2+\beta_{k,1}^2+\dots+\alpha_{k,r}^2+\beta_{k,r}^2\geq (\alpha_{k,0}+B\mathbf{u}_k+\dots+B\mathbf{u}_{k+n-1})^2+p_1^2\alpha_{k,1}^2+p_1^2\beta_{k,1}^2+\dots+p_r^2\alpha_{k,r}^2+p_r^2\beta_{k,r}^2$ and $()$.
%
%\end{proof}
% Lol wrong... Doesn't make sense this lemma at all...
%
\subsection{Energy evolution due to computations}
\label{sec:computations-model}

@@

\begin{thm}[State output linearity]\label{thm:state-vs-energy}
  Consider the mission from Definition~\ref{def:mission}, the valid mission from~\ref{def:valid}, assume Assumption~\ref{assm:periodic} holds, the model behaves ideally ($\mathbf{w}=\mathbf{0},v=0$), the initial energy coefficients state is $\mathbf{q}_0=\begin{bmatrix}
    y_0^m/j & (1/2)y_0^m/j & \cdots & (1/2)y_0^m/j
  \end{bmatrix}^T$ where $y_0^m\in\mathbb{R}_{>0}$ is an initial measurement\footnote{$y_0^m$ can be the initial measurement or the measurement from a previous instance of the algorithm}, and the mission is valid.
  Then, the instantaneous energy consumption $y_k$ is a linear combination of the state $\mathbf{q}_k$.
\end{thm}
\begin{proof}
  The proof is based on mathematical induction. 
  \emph{(Base case)}. We proof that $y_0=y_0^m$. Recall the definition of the state in Equation~(\ref{eq:state-details}). The output is $y_{0}=\alpha_{0,0}+\alpha_{0,1}+\dots+\alpha_{0,r}=y_0^m/j+(1/2)y_0^m/j+\cdots+(1/2)y_0^m/j=y_0^m$.

  \emph{(Induction step)}. By inspection of Equation~(\ref{eq:state-perf}), the output at instant $k$ can be expressed $y_{k}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)\alpha_{0,1}+\dots+p_r(n)\alpha_{0,r}$, where 
  \begin{equation}
    p_r(k):=\begin{cases}
      \prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for even }k\\
      (r/\xi)\prod_{i=1}^{k/2}{r^3/\xi^3}&\text{ for odd }k
    \end{cases},
  \end{equation}
  Using $\mathbf{q}_0$ leads to $y_{k}=(y_0^m/j+B\mathbf{u}_0+\dots+B\mathbf{u}_{k-1})+p_1(k)(1/2)y_0^m/j+\dots+p_r(k)(1/2)y_0^m/j=y_{k}^m$.

  We prove now that the instantaneous energy consumption at $k+1$ is still a linear combination of the state $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)\beta_{k,1}+\dots+(r/\xi)\beta_{k,r}$. Notice that the coefficients $\alpha,\beta$ have an equivalent evolution (indeed this allows to simulate the periodicity) and $\beta_{k,r}=p_r(k)\beta_{0,r}$. The output can be expressed $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+(1/\xi)p_1(k)\beta_{0,1}+\dots+(r/\xi)p_r(k)\beta_{0,r}$. The expression is equivalent to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)\beta_{0,r}+\dots+p_r(k+1)\beta_{0,r}$. Using $\mathbf{q}_0$ leads to $y_{k+1}=(\alpha_{0,0}+B\mathbf{u}_0+\dots+B\mathbf{u}_{k})+p_r(k+1)(1/2)y_0^m+\dots+p_r(k+1)(1/2)y_0^m=y_{k+1}^m$, alike the previous statement ($y_k^m=y_{k+1}^m$), but at instant $k+1$.
\end{proof}
